\ttitle

### 2015-08-09 Chapters/Discussion.tex
Major changes as below
- Thesis summary completed
- Many changes to thesis.cls and main.tex to format abstract page and university url, etc
- Update Intro-body comp - measuring body comp
- Zot.bin backed up and updated
- Conclusion chapter title renamed to Discussion
- It is 01:40 am - Have listened to Dr. Dre, Snoop Dogg and Eminem all day
- 2 shots of Jura and I am knackered yet sleepless after 2 strong coffees
Discussion - 2/3 complete
- Minor changes in introduction
- Fixed effing error in zot.bib as a consequence of error in junejo abstract with Tex commands embedded - WHY???
- Fixed a fe

\chapter{Conclusion}
\label{ch_conclusion}

\lhead{Chapter \ref{ch_conclusion}. \emph{Conclusion}} % This is for the header on each page - perhaps a shortened title

@@

This is the easy bit

>>>>

\chapter{Discussion}
\label{ch_discussion}

\lhead{Chapter \ref{ch_discussion}. \emph{Discussion}} % This is for the header on each page - perhaps a shortened title

@@

The overall aim of the thesis was to examine the relationships between cardiopulmonary exercise physiology, obstructive jaundice, systemic inflammation, body composition and short and long-term outcomes after major pancreatic surgery.

A secondary aim of the thesis was to clarify the factors that affect cardiopulmonary exercise physiology and provide a better understanding of the complex pathophysiology in these patients that is a consequence of the interaction of the patient's chronic conditions with the acute derangements brought on by pancreatic disease, including obstructive jaundice.

The results of the present work have demonstrated that cardiopulmonary exercise testing provides an objective, reproducible method of identifying high risk patients who are more likely to develop complications, stay longer in hospital and are less likely to receive adjuvant therapy where the underlying pathology is a malignancy. These results have since been replicated by other authors examining the role of cardiopulmonary exercise testing in pancreatic surgery. \parencite{ausania_effects_2012, ausania_double_2012, junejo_cardiopulmonary_2014}

Equally important is the observation that preoperative obstructive jaundice did not impair aerobic capacity as measured by cardiopulmonary exercise testing. We are aware of only one other published study looking at cardiopulmonary exercise testing and peripheral oxygen extraction in jaundiced versus non-jaundiced patients undergoing pancreaticoduodenectomy. Junejo and co-workers reported that peripheral oxygen extraction was normal during exercise in patients with malignant obstructive jaundice.\parencite{junejo_peripheral_2014} 
Routine preoperative biliary drainage is no longer recommended before a pancreaticoduodenectomy. Several studies have shown that preoperative biliary drainage increases the incidence of postoperative complications, especially infective complications. \parencite{van_der_gaag_preoperative_2010, arkadopoulos_preoperative_2014, fujii_preoperative_2015, furukawa_negative_2015}
The results reported in this thesis in conjunction with recently published clinical studies support the view that routine preoperative biliary drainage should no longer be performed in all patients scheduled to undergo a pancreaticoduodenectomy.

We also observed that overweight and obese patients had significantly lower $\dot{V}_{O_2}$AT and $\dot{V}_{O_2}$Peak in spite of no significant increase in known cardiac or respiratory comorbidities. The analysis of the relationship between body composition and preoperative cardiopulmonary exercise testing has not been reported before in surgical patients. These results demonstrate that interpretation of cardiopulmonary exercise test parameters in patients with a high BMI must be made with caution, especially when such parameters have been corrected for the patient's total body weight. With the significant increase in the proportion of obese patients undergoing major surgery and the presence of sarcopenic-obesity in patients with pancreatic cancer, poor performance at cardiopulmonary exercise testing may not necessarily be related to cardiac or pulmonary function. The loss of skeletal mass and spurious correlations due to correction for total body weight may partly explain the low $\dot{V}_{O_2}$ in these patients.

Recognition of these factors is important not only in patient selection and informed consent, but also in instituting the appropriate interventions as part of prehabilitation programmes. In a recent study of 8266 patients undergoing pancreaticoduodenectomy in the United States, Tzeng and co-workers reported that a third (3033) were of borderline fitness as a consequence of advanced age ($>$ 80), poor performance status, weight loss $>$ 10\%, pulmonary disease, recent myocardial infarction/angina, stroke history, and/or preoperative sepsis. The authors report that major complications (31.3 vs. 26.2\%) and mortality (4.1 vs. 2.3\%) were greater in these patients.\parencite{tzeng_morbidity_2014} 
The authors recommend that surgeons identify these patients early, institute interventions to optimise their comorbidities and enrol these patients for prehabilitation.

West and co-workers used prehabilitation to return aerobic capacity to baseline levels in patients with locally advanced rectal cancer undergoing neo-adjuvant chemoradiotherapy.\parencite{west_effect_2015} 
Moderate aerobic and resistance exercises and protein supplementation started 4 weeks before surgery was noted to improve postoperative functional exercise capacity in patients undergoing colorectal cancer surgery.\parencite{gillis_prehabilitation_2014}
Exercise programs as short as 4 weeks in duration have been reported to improve aerobic capacity measured objectively by cardiopulmonary exercise testing by upto 10\% which can potentially move approximately 30\% of high risk patients into the low risk category.\parencite{dunne_pmo-029_2012}

Early recognition of patients at increased risk of postoperative complications facilitates prompt initiation of appropriate treatment and judicious allocation of critical care resources. Moreover, identification of patients who are unlikely to develop a major postoperative complication allows their progress on enhanced recovery pathways with the benefits of rapid recovery, reduced morbidity and early discharge. These patients are also more likely to receive adjuvant therapy without undue delay. Recognition of these low risk patients helps improve outcomes, reduces hospital costs and releases valuable resources for the care of high risk patients. The results reported in Chapter [ss] demonstrate the value of early post-operative C-reactive protein in identifying patients who are more likely to develop an infective complication. The results show that CRP is only useful in the absence of a postoperative pancreatic fistula. The combination of low drain amylase and low CRP on the third postoperative day identifies patients who do not have a pancreatic fistula and are less likely to develop an infective complication.

### 2015-08-09 main.tex
Discussion - 2/3 complete
- Minor changes in introduction
- Fixed effing error in zot.bib as a consequence of error in junejo abstract with Tex commands embedded - WHY???
- Fixed a few minor issues with main.tex

Cardiopulmonary exercise testing is becoming an increasingly popular tool in the preoperative risk assessment of the surgical patient. However, very little work has been done to investigate the role of cardiopulmonary exercise test in patients scheduled to undergo pancreaticoduodenectomy. The impact of jaundice, sytemic inflammation and other preoperative clinicopathological characteristics of the patient on their cardiopulmonary exercise physiology has not been studied in detail before in this cohort of patients. Moreover, the impact of these factors on long-term survival is also unknown.

@@

\textbf{Chapter \ref{ch_cpet_outcomes}} reports on the role of cardiopulmonary exercise testing in predicting postoperative complications. The results demonstrate that patients with anaerobic threshold less than 10 mls/kg/min were more likely to develop a postoperative pancreatic fistula, stay longer in hospital and less likely to receive adjuvant therapy after pancreaticoduodenectomy. These results emphasise the importance of excellent aerobic fitness to improve postoperative outcomes and provide a potential target for future prehabilitation programmes.

\textbf{Chapter \ref{ch_cpet_jaundice}} evaluates the relationship between cardiopulmonary exercise physiology and other clinicopathological characteristics of the patient. In a detailed analysis of cardiopulmonary exercise test parameters in jaundiced versus non-jaundiced patients, the results in this chapter demonstrate that obstructive jaundice does not impair cardiopulmonary exercise physiology. This further supports emerging evidence in contemporary literature that jaundiced patients can proceed directly to surgery without underoing preoperative biliary drainage. The results of this study also show an interesting inverse relationship between body mass index and anaerobic threshold which is analysed in more detail in Chapter 3.

@@

\textbf{Chapter \ref{ch_survival}} analyses the relationship between preoperative comorbidity including cardiopulmonary exercise test and long-term survival in patients with pancreatic ductal adenocarcinoma undergoing pancreaticoduodenectomy. The results of this chapter suggest that cardiopulmonary exercise testing parameters are not useful in predicting long-term survival. However, a composite score of preoperative physiology as measured by the POSSUM Physiology score was associated with survival.

@@

}
\clearpage

@@

% Include the chapters of the thesis as separate files from the Chapters folder
\input{Chapters/Introduction} 		%1
%\input{Chapters/CPET_Outcomes} 	%2
%\input{Chapters/CPET_Jaundice} 	%3
%\input{Chapters/BodyComp}			%4
%\input{Chapters/CPET_Survival}		%5
%\input{Chapters/CRP_Complications}	%6
%\input{Chapters/Discussion}		%7

@@

%\input{Appendices/AppendixExcelMacros}
%\input{Appendices/AppendixCPETRawData}
%\input{Appendices/AppendixC}

@@

\lhead{\emph{Bibliography}} % Change the page header to say "Bibliography"

%\bibliographystyle{unsrtnat} % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\printbibliography

\listoftodos

>>>>

Cardiopulmonary exercise testing is becoming an increasingly popular tool in the preoperative risk assessment of the surgical patient. However, very little work has been done to investigate the role of cardiopulmonary exercise testing in predicting complications after pancreaticoduodenectomy. The impact of jaundice, systemic inflammation and other preoperative clinicopathological characteristics on cardiopulmonary exercise physiology has not been studied in detail before in this cohort of patients.

@@

\textbf{Chapter \ref{ch_cpet_outcomes}} reports on the role of cardiopulmonary exercise testing in predicting postoperative complications after pancreaticoduodenectomy. The results demonstrate that patients with $\dot{V}_{O_2}$AT less than 10 ml/kg/min are more likely to develop a postoperative pancreatic fistula, stay longer in hospital and less likely to receive adjuvant therapy. These results emphasise the importance of excellent aerobic fitness to recover from the operative stress of major surgery without significant morbidity. Cardiopulmonary exercise testing may prove useful in selecting patients for intensive prehabilitation programmes as well as for other optimisation measures to prepare them for major surgery.

\textbf{Chapter \ref{ch_cpet_jaundice}} evaluates the relationship between cardiopulmonary exercise physiology and other clinicopathological characteristics of the patient. In a detailed analysis of cardiopulmonary exercise test parameters in jaundiced versus non-jaundiced patients, the results in this chapter demonstrate that obstructive jaundice does not impair cardiopulmonary exercise physiology. This further supports emerging evidence in contemporary literature that jaundiced patients can proceed directly to surgery without preoperative biliary drainage. The results of this study also show an interesting inverse relationship between body mass index and anaerobic threshold which is analysed in more detail in Chapter \ref{ch_bodycomp}.

@@

\textbf{Chapter \ref{ch_survival}} analyses the relationship between preoperative comorbidity including cardiopulmonary exercise test and long-term survival in patients with pancreatic ductal adenocarcinoma undergoing pancreaticoduodenectomy. The results of this chapter suggest that cardiopulmonary exercise testing parameters are not useful in predicting long-term survival. However, a composite score of preoperative comorbidity as measured by the POSSUM Physiology score appears to predict long-term survival.

@@

@@

% Include the chapters of the thesis as separate files from the Chapters folder
\input{Chapters/Introduction} 		%1
\input{Chapters/CPET_Outcomes} 	%2
\input{Chapters/CPET_Jaundice} 	%3
\input{Chapters/BodyComp}			%4
\input{Chapters/CPET_Survival}		%5
\input{Chapters/CRP_Complications}	%6
\input{Chapters/Discussion}		%7

@@

\input{Appendices/AppendixExcelMacros}
\input{Appendices/AppendixCPETRawData}
%\input{Appendices/AppendixC}

@@

\lhead{\emph{Bibliography}} % Change the page header to say "Bibliography"
%\bibliographystyle{unsrtnat} % Use the "unsrtnat" BibTeX style for formatting the Bibliography
\printbibliography

\clearpage
\listoftodos
